The Evolution of Heavy-Ion Physics: A Data-Driven Analysis of Quark Matter Conferences

### 2025-03-24 QM/paper.tex
2025 missing

>>>>

The overall participant attendance (shown with the red line in the top panel) demonstrates substantial fluctuation over the years, with certain conferences attracting significantly larger audiences than others. Notably, the significantly lower attendance in 2022 can be attributed to the COVID-19 pandemic, which continued to impact international travel and large gatherings. This conference was held during a period of transition from virtual to in-person events, with many institutions still maintaining travel restrictions. Excluding this pandemic-affected outlier, participant numbers do not always directly correlate with the total number of presentations, suggesting that factors such as conference location, accessibility, concurrent events, and broader community interest play important roles in determining attendance. The highest attendance periods often coincide with conferences held in major research hubs or following significant experimental milestones.
